\documentclass[12pt]{article}
\title{R\'esum\'e}
\author{Gus Cantieni}
\renewcommand{\familydefault}{\sfdefault}

% packages
\usepackage{textcomp} % kill bullet warnings
\usepackage{titlesec} % redef sections
\usepackage{enumitem} % def list spacing
\usepackage{titling}
\usepackage{multicol}
%\usepackage[margin=0.5in]{geometry}

\headheight=-30pt
\textheight=674pt


% redefine commands and set options
\renewcommand{\maketitle}{
	\begin{center}
		{\huge\bfseries Gus Cantieni}
		\vspace{0.25em}

		gus\_cantieni@brown.edu --- github.com/gcantieni

		\vspace{0.75em}
		%\noindent\makebox[\linewidth]{\rule{\paperwidth}{0.4pt}}
		%\titlerule
	\end{center}
}

\pagenumbering{gobble}

\titlespacing{\subsection}
{0em} {1em} {0em}

\titlespacing{\section}
{0em} {0em} {1em}

\titleformat{\section}
{\huge\bfseries\lowercase}
{}
{1em}
{}[\titlerule]

\titleformat{\subsection}
{\Large\bfseries\lowercase}
{}
{0em}
{}


\setlist{nosep} % remove item spacing

% Dimensions
\topmargin=0.0in %length of margin at the top of the page (1 inch added by default)
%\oddsidemargin=0.0in %length of margin on sides for odd pages
%\evensidemargin=-0.5in %length of margin on sides for even pages
\textwidth=5in %How wide you want your text to be
%\marginparwidth=0.5in
%\headheight=0pt %1in margins at top and bottom (1 inch is added to this value by default)
\headsep=0pt %Increase to increase white space in between headers and the top of the page
%\textheight=9.0in %How tall the text body is allowed to be on each page
\itemsep=0in
\parsep=0in

\begin{document}

\maketitle

\vspace{1em}
\fontsize{12}{15}\selectfont
\noindent
To Amy Seibel, 
\vspace{1em}

\noindent
There's nothing I like more than to design computer systems, build layers of abstraction, and refactor tangled code to make it sparse and lean. I am a computer science major studying at Brown University, with a specialties in AI and computer systems, and with work experience in full stack web development and open source, non-profit technology. I find helping the code base shrink, bugs disappear, and unit tests go from red to green uniquely satisfying. Software development, which began as a purely academic pursuit, for me has grown into a source of value, satisfaction, and joy, and I think we can use it to make the world a better place.
\vspace{0.75em}

\noindent
Dell would give me a perfect opportunity to practice these skills, and I love the company. My daily driver is a Dell XPS13, and I've love the fact that Dell sells Developer Editions of many of its products. I am also well qualified to the position. I am a junior currently studying to get a Bachelors degree in Computer Science. While working remotely over last summer with Open Learning Exchanged (OLE), I demonstrated strong self-motivation through my consistent work ethic despite the distance and flexible schedule. I also learned a DevOps-oriented style of development, with constant version releases and quick turn around. 

\vspace{0.75em}
\noindent
At both school, and working at Open Learninig Exchange, I showed my ability to work in a fast-paced, collaborative environment: OLE practiced pair programming, and we completed my upper level Computer Science projects in groups. In both these settings, I was able to give and take constructive criticism, keep groups organized and on-track, and take on significant challenges. 

\vspace{0.75em}
\noindent
I use Linux, so am intimately familiar with UNIX principles and utilities. I also have experience working in Go, Java, and JavaScript. If you want a display of my enthusiasm, just ask me about Irish music, or my love of baking.  

\vspace{0.75em}
\noindent
I hope you will consider me for this position. Attached is my resume---feel free to reach out to me at my school email, gus\_cantieni@brown.edu, or my personal phone, 413-522-4103, if I qualify for this or any other position.


\vspace{2em}
\hfill Sincerely,

\hfill Gus Cantieni
\end{document}

